---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Package BootstrapTests

<!-- badges: start -->
<!-- badges: end -->

This package BootstrapTests implements several methods to perform bootstrap-based 
hypothesis testing procedures on three statistical problems: independence testing,
testing the slope in a linear regression setting, and goodness-of-fit testing.

## Installation

You can install the development version of BootstrapTests from [GitHub](https://github.com/)
using the `devtools` package with:

``` r
# install.packages("devtools")
devtools::install_github("AlexisDerumigny/BootstrapTests")
```

## Examples

The following three subsections will showcase the use of the \code{BootstrapTests}
package for the independence testing, testing the slope in a linear regression setting, 
and goodness-of-fit testing. In particular, we will show the use of the functions:"

- \code{perform_regression_test.R}
- \code{perform_independence_test.R}
- \code{perform_GoF_test.R}

### Independence testing

```{r example independence}
library(BootstrapTests)
## basic example code
 n = 100

 # Under H1
 X1 = rnorm(n)
 X2 = X1 + rnorm(n)
 result = perform_independence_test(X1, X2, nBootstrap = 100)
 result$pvals_df
 
 # Under H0
 X1 = rnorm(n)
 X2 = rnorm(n)
 result = perform_independence_test(X1, X2, nBootstrap = 100)
 result$pvals_df
```


### Slope testing in linear regression setting

```{r example linear regression}
library(BootstrapTests)
## basic example code

 n = 100
  # Under H1
  X_data = rgamma(n,2,3)
  result_H1 = perform_GoF_test(X_data, nBootstrap = 30)
  result_H1
  
   # Under H0
  X_data = rnorm(n)
  result_H0 = perform_GoF_test(X_data, nBootstrap = 30)
  result_H0
```


### Goodness-of-fit testing

```{r example GOF}
library(BootstrapTests)
## basic example code

 n = 100
  # Under H1
  X_data = rgamma(n,2,3)
  perform_GoF_test(X_data, nBootstrap = 30)
  
   # Under H0
  X_data = rnorm(n)
  perform_GoF_test(X_data, nBootstrap = 30)
```


## References

To be included



